Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-16 paper/main.tex
rewrite plan

\begin{itemize}
    \item tables: round p-values to ? MIH: I would say 4 digits, but I can find internet
      recommendations for 3. That would mean anything less than 0.001 is reported as '<.001',
      and the rest as the precise value. This should only apply to corrected p-values.
      For an uncorrected p-value 0.001 is very high.
\end{itemize}

@@

\noindent Data Citations, Code Availability
\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scientific Data analysis paper
\end{itemize}

@@

Raw data, analysis scripts, and results: TBA. Zenodo (registered but zipped)
vs. OSF (datalad dataset but probably unregistered)

>>>>

\begin{itemize}
    \item tables: I (initially) rounded p-values to <.00001
\end{itemize}

@@

\noindent Data Citations, Code Availability
\begin{itemize}
    \item draft for Data Citation is done
    \item draft for Code and Data Availability is done (other analysis paper do
        it pretty amateurish); will look at the ``how to write an excellent
        data availability statement'' at springernature.com
\end{itemize}

@@

% Zenodo (registered but zipped) vs. OSF (datalad dataset but probably
% unregistered)
Raw data, analysis scripts to generate the results from the raw data as well as
the results are available from *TBA*, and accessible as Datalad
(RRID:SCR_003931) datasets.
